### 2017-12-24 icde/revision/sec-intro.tex

Query independent ranking of scholarly articles remains challenging~\cite{wsdmcup}, although there exists quite a bit of work on scholarly article ranking, \eg~\cite{Garfield471,Liang16AAAI,Jiang12-MRank,Waltman2014}.
Most previous work exploits the time-dependent information of scholarly data in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, which fails to capture the diverse citation patterns of individual articles~\cite{Chakraborty15}.
Further, to our knowledge, little concern has been paid to dynamic scholarly article ranking except \cite{GhoshKHLL11} with a strong and impractical assumption that there are no citations between papers published in the same years.
%\marked{Finally, the bias caused by the dynamic nature of data has never been exploited in scholarly article ranking}.

>>>>

Query independent ranking of scholarly articles remains challenging~\cite{wsdmcup}, although there exists quite a bit of work on scholarly article ranking, \eg~\cite{Garfield471,Liang16AAAI,Jiang12-MRank,Waltman2014}.
Most previous work exploits the time-dependent information of scholarly data in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, which fails to capture the diverse citation patterns of individual articles~\cite{Chakraborty15}.
Further, to our knowledge, little concern has been paid to dynamic scholarly article ranking except \cite{GhoshKHLL11} with a strong and impractical assumption that there are no citations between articles published in the same years.
%\marked{Finally, the bias caused by the dynamic nature of data has never been exploited in scholarly article ranking}.
